---
title: "813 Data exercise 1"
author: "X. Zhang"
date: "January 25, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo=FALSE}
library(tidyverse)
library(haven)
EX1_813_file <- "https://github.com/14XZ/xzhang-811/raw/master/PS835_EX1_35435.dta" #seed: 35435
EX1_813 <-read_dta(EX1_813_file) 
```


```{r}
ggplot(EX1_813, aes(x = terms, y = Leg_Act)) + geom_point()
```
plotting legislative acts against terms, graph show no clear pattern.

```{r}

leg_mod <- lm(Leg_Act ~ terms, data = EX1_813)
summary(leg_mod)
```
intercept: 7.57; coefficient of terms variable: 0.17

```{r}
EX1_813$residual <- resid(leg_mod)
EX1_813$pred <- predict(leg_mod)
```

```{r plot the residual}
ggplot(EX1_813, aes(x = terms, y = Leg_Act)) + geom_point()
```

```{r correlation between observed and predicted value of Leg_Act}
correlation <- cor(EX1_813$Leg_Act, EX1_813$pred)
```
correlation of observed legislative act and predicted value is 0.041

```{r compare the aforementioned correlation sqaured and R^2 output of the regression model}

summary(leg_mod)$r.squared

c.sq <- correlation^2
```
correlation squared (c.sq) and r square of the model is the same.

```{r hypothesis test}
summary(leg_mod)
```

# Discussion:
Set the confidence level at 5% , the p-value of terms variable would be less than 0.05
model output suggest the term variable has a p-value of 0.86 > 0.05;
Thus, the null hypothesis of b=0 cannot be rejected.
